---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# varifinder

<!-- badges: start -->
<!-- badges: end -->

Monitoring physical activity and other factors of the patients after administrating anesthesia is important because it can have several effects on the body. It is also necessary to detect the time points when the values of these variables change. In general, the total anesthesia period is clinically divided into many phases, where the large deviation of the values within same phase is frequently observed, specially in pediatric patient data. The goal of `varifinder` is to calculate the variability ratio index (VARI) to compare the number of detected change points between different clinical phases in retrospective data.

## Installation

You can install the development version of varifinder from [GitHub](https://github.com/) with: (noormuhammadkhan)

``` r
# install.packages("devtools")
devtools::install_github("noormuhammadkhan/varifinder")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example, eval=FALSE}
library(varifinder)
 # Prepare a dummy data set
 variable <- rnorm(100, 50, 5)
 time <- c(seq(1,30), seq(1, 40), seq(1,20), seq(1,10))
 phase <- rep(factor(c(1, 2, 3, 4)), c(30, 40, 20, 10))
 
 # Identify the VARI
 varifinder(variable, phase, time)
```

